On Adding Pattern Matching to Haskell-based Deeply Embedded Domain Specific Languages\\ \large{Not For Distribution}

### 2020-08-01 paper/paper.tex
Citation for SSA
Better comparision to SSA
wibble

This backend is based on a globally unique name generator. Similar to
SSA form, a new C variable is created for each Haskell subexpression.
It differs from SSA, however, in that these variables can be assigned multiple
times. In particular, a variable can be assigned in multiple branches of
an \ttt{if} statement or inside of a \ttt{while} loop. This simplifies
the implementation, as $\phi$ nodes are not needed.

@@

In the flowchart given in Figure~\ref{fig:CorePlugin}, the names in parentheses in a node refers
to the names of transformations given in the rewrite rules in Figure~\ref{fig:Rewrites}. In Figure~\ref{fig:Rewrites},
$\varepsilon$ represents an empty term (in the context of the term rewriting system used in that Figure). Calls
to \ttt{unrep :: E a -> a} are only used internally and will not exist in
the final result of the transformation.

>>>>

This backend is based on a globally unique name generator. A new C variable is created for each Haskell subexpression.
The result appears similar to static single assignment (SSA) form~\cite{Rosen:1988:SSA}.
It differs from SSA, however, in that these variables can be assigned multiple
times. In particular, a variable can be assigned in multiple branches of
an \ttt{if} statement or inside of a \ttt{while} loop. This simplifies
the implementation, as $\phi$ nodes are not needed.

@@

In the flowchart given in Figure~\ref{fig:CorePlugin}, the names in parentheses in a node refer
to the names of transformations given in the rewrite rules in Figure~\ref{fig:Rewrites}. In Figure~\ref{fig:Rewrites},
$\varepsilon$ represents an empty term (in the context of the term rewriting system used in that Figure). Calls
to \ttt{unrep :: E a -> a} are only used internally and will not exist in
the final result of the transformation.
